---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# github.traffic

{github.traffic} lets you retrieve github traffic information + some related info such
as stars and watchers.

github only provides data for the last 14 days but this package helps you build
and update a local database wih this info. You can also schedule he update to
run at a chosen frequency (Windows only at the moment)


## Installation

Install with:

``` r
remotes::install_github("moodymudskipper/github.traffic")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(github.traffic)
```

Fetch last 14 days of data for a given repo (or a vecor of repos) :

```{r}
fetch_github_traffic("moodymudskipper/flow")
```

Or all repos from a given owner (excluding forks and private repos), this
might take a bit of time if you have many repos. You can also provide a 
character vector containing a mix of repos and owners.

```{r}
fetch_github_traffic("moodymudskipper")
```

Create or update a local DB manually with this info

```{r}
update_github_traffic_db("moodymudskipper") 
```

Or automate this process so it's updated at the chosen frequency (daily by default)

```{r}
schedule_github_traffic_db_updates("moodymudskipper")
```

Then retrieve your data by running:

```{r}
github_traffic_db()
```
